Active Learning for SAT Solver Benchmarking {\large (extended and revised version)}

### 2024-05-27 paper_jar/paper.tex
minor changes

In contrast, the ranking stopping criterion is less sophisticated than the previous one.
In this case, active learning terminates when the ranking induced by the model's predictions (Equation~\eqref{eq:rankingeq}) has remained unchanged within the last~$l$~iterations.
While the concrete values of the predicted score $s_{\hat a}$ may still change, the induced ranking is of sole interest in this criterion.

@@

In our experiments, we work with the dataset of the SAT~Competition~2022 Anniversary Track~\cite{sat2022}.
This dataset consists of 5355 instances with corresponding runtimes of 28 sequential SAT solvers.
For predictions within our framework, we also use a database of 56 instance features\footnote{\url{https://benchmark-database.de/getdatabase/base_db}} from the Global Benchmark Database~(GBD) by Iser~et~al.~\cite{IserS18}.
They include instance size features and node distribution statistics for several graph representations of SAT instances, and are primarily inspired by the SATzilla~2012 features described in~\cite{features}.
All features are numeric and have no missing values.
We drop 10 of the 56 features due to zero variance.
In total, the prediction models have access to 46 instance features and 27 out of 28 runtime features, excluding the respective new solver~$\hat{a}$.

@@

For reproducibility, our source code and data are available on GitHub (see footnotes in Section~\ref{sec:intro}).
Our code is implemented in \textsc{Python} using \emph{scikit-learn}~\cite{scikit-learn} for making predictions, and \emph{gbd-tools}~\cite{IserS18} for retrieving SAT instances.

>>>>

In contrast, the ranking stopping criterion is less sophisticated than the previous one.
In this case, active learning terminates when the ranking induced by the model's predictions (cf.~Equation~\eqref{eq:rankingeq}) has remained unchanged within the last~$l$~iterations.
While the concrete values of the predicted score $s_{\hat a}$ may still change, the induced ranking is of sole interest in this criterion.

@@

In our experiments, we work with the dataset of the SAT~Competition~2022 Anniversary Track~\cite{sat2022,zenodoanniversarytrack}.
This dataset consists of 5355 instances with corresponding runtimes of 28 sequential SAT solvers.
For predictions within our framework, we also use a database of 56 instance features\footnote{\url{https://benchmark-database.de/getdatabase/base_db}} from the Global Benchmark Database~(GBD)~\cite{GBD24paper}.
They include instance size features and node distribution statistics for several graph representations of SAT instances, and are primarily inspired by the SATzilla~2012 features described in~\cite{features}.
All features are numeric and have no missing values.
We drop 10 of the 56 features due to zero variance.
In total, the prediction models have access to 46 instance features and 27 out of 28 runtime features, excluding the respective new solver~$\hat{a}$.

@@

For reproducibility, our source code and data are available on GitHub (see footnotes in Section~\ref{sec:intro}).
Our code is implemented in \textsc{Python} using \emph{scikit-learn}~\cite{scikit-learn} for making predictions, and \emph{gbd-tools}~\cite{GBD24paper} for retrieving SAT instances.
